Chemically Selective Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-06-25 Ben_Manuscripts/transport/response_to_reviewers.tex

    \item \begin{quote}
    \textit{The explanation regarding the transport of water molecules in the tail 
    region relative to water molecules in the pore region for the 5\% (by weight) 
    water system that occurs in the paragraph that begins at the end of page 20 is
    rather unsatisfying. While certain statistics are pointed to, there is not a 
    full explanation provided here. Expanding this point in order would strengthen
    the manuscript.}
    \end{quote}

    Author reply: We thank the reviewer for pushing us to strengthen our description
    of tail water transport in the 5 wt\% water system, as our point could be 
    confusing without proper explanation.

    Original text: ``This anomaly is likely a consequence of lower density in the
    distal tails relative to the pores, leading to faster diffusion in the tails,
    as well as slowed diffusion of water molecules in the pores via hydrogen 
    bonds with other water molecules and association with sodium ions. Water molecules are 
    less likely to hydrogen bond with each other while in the distal tail region since they
    are interspersed between chains, while those in the pores stay in close proximity to 
    each other. We observed about 9 times more hydrogen bonding between water molecules 
    near the pore center versus those in the distal tail region. Additionally, an average 
    of 65\% of water molecules in the pores of the 5 wt\% water system are associated
    with a sodium ion each frame compared to 44\% in the 10 wt\% water system. There is a
    negligible amount of hydrogen bonds between water molecules and monomer head groups.

    New text: ``This behavior is likely due to the
    much more crowded pore environment in the 5 wt\% versus the 10 wt\% water system. 
    Monomer head groups are concentrated about 2~\AA~closer to the pore centers in the
    5 wt\% versus the 10 wt\% water system (see Figure~\ref{M-fig:component_densities})
    which leaves less space for water molecules and restricts their movement among the 
    relatively immobile monomer head groups. The consequently high energetic barrier 
    to diffusion enhances the favorability of associative interactions between water
    and monomer components. The 95th percentile lifetime of hydrogen bonds between 
    water molecules located near the pore center is 2.1 ns in the 5 wt\% system compared
    to 0.5 ns in the 10 wt\% system. However, since we only saved simulation output 
    every 0.5 ns, it is likely that the true hydrogen bond lifetimes in the 10 wt\% 
    system are shorter than this value. Additionally, there are more frequent and longer
    periods of association between water and sodium ions. An average of 65\% of water 
    molecules in the pores of the 5 wt\% water system associate with a sodium ion each
    frame compared to 44\% in the 10 wt\% water system.There are about half as many water
    molecules in the 5 wt\% water system which allows a larger fraction of them to 
    associate with sodium ions. The lifetime of associations between sodium ions and 
    water is 7.5 ns and 3.0 ns in 5 and 10 wt\% water systems respectively.``

@@

	\textit{The water model used by the authors was not explicitly mentioned in Section 2 
	of the paper. From the Results section it is inferred that they used the TIP3P water model.
	The authors should explicitly mention their choice of water model in Section 2, and 
	justify this choice.}

	\end{quote}

	Author reply: We thank the reviewer for pointing out that we are missing this essential detail.
	We have added the following text to section 2.1 of the main text:

	New text: ``We simulated water molecules using the TIP3P water model because it is
	the water model that GAFF and other AMBER family parameters have been optimized
    with.''
%    computationally efficient and reasonably reproduces water's physical properties
%    at 300K, the temperature of our simulations.``

### 2019-06-25 Ben_Manuscripts/transport/Final_Draft.tex
Made sure response to reviewers matches main text

\title{Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

@@

  The uniform size and complex chemical topology of the pores formed by
  self-assembled amphiphilic molecules such as liquid crystals make them
  promising candidates for selective separations.
  %that 
  %constitute cross-linked inverted hexagonal (H\textsubscript{II})
  %phase lyotropic liquid crystal (LLC) membranes make them promising
  %candidates for selective separation membranes. 
  %MRS3: I do worry that the above makes it look like we are not acknowledging
  %the formulation problems.  Maybe something like: ''models of how chemically
  %selective separation membranes could can function''?  So the focus is more
  %on the science that these membranes could reveal, rather than saying they
  %are good membranes now?  Then we talk about new membranes at the end of the
  %introduction. Thoughts? I didn't go ahead and make  the change since it
  %needs a bit more thought.  I'm open to other ways to reformulate.  Some of
  %this thinking will percolate into the rest of the introduction as well.
  In this work, we observe transport of water, sodium ions and 20 small polar
  solutes within the pores of a lyotropic liquid crystal (LLC) membrane using
  atomistic molecular simulations. We find that the transport of a species is
  dependent not only on molecular size, but on chemical functionality as well.
  The membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe that all
  solutes perform intermittent hops between lengthy periods of entrapment. Three
  different trapping mechanisms are responsible for this behavior. First, solutes
  that drift out of the pore can become entangled among the dense monomer tails.
  Second, solutes can donate hydrogen bonds to the monomer head groups. Third,
  solutes can coordinate with sodium counter ions.  The degree to which a solute
  is affected by each mechanism is dependent on the chemical functionality of the
  solute. Using the insights developed in this study, we can begin to think about
  how to redesign existing LLC membranes in order to perform solute-specific
  separations.

@@

  All of these separations are possible in part with current commercial
  membrane separation techniques, but all still suffer from serious drawbacks.
  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial
  membrane separations of small molecules.~\cite{warsinger_review_2018} RO
  membranes are typically dense polymer matrices that separate solutes based on
  differences in their solubility and permeability in the membrane
  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
  selective separations, high feed pressures and thus large amounts of energy are
  necessary in order to generate a useful permeate
  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
  nm-sized pores which can give the same permeate flux as RO with lower applied
  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
  size, limiting their selectivity.~\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

%  A membrane with the
%  selectivity of an RO membrane and the permeability of an NF membrane would
%  offer a significant improvement to current commercial membrane technology.
%  Nanostructured membranes offer the potential for molecular-level design 
%  which could overcome the limitations faced by conventional membrane 
%  technologies. One can create dense arrays of well-defined uniform-sized
%  \begin{itemize}
%    \item Mitigation of stochastic aspects of membrane synthesis
%    \item Well-defined and uniform pores increase selectivity
%    \item Solute-specific separations.
%  \end{itemize}

% re-outline from here.

%  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
%  membranes are nanostructured membranes that may be able to achieve the
%  selectivity of RO membranes while maintaining the high permeability
%  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
%  phase is formed when LLC monomers self-assemble into hexagonally packed
%  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
%  cross-linking of the hexagonal mesophases yields a mechanically strong
%  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
%  enforce a strict molecular-size cut-off while the hexagonal geometry is 
%  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
%  because the LLC monomers are salts, Donnan exclusion plays a role in 
%  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}

  %BJC4: generalized to amphiphilic self-assembled structures.
  Under the right conditions, amphiphilic molecules can self-assemble into
  ordered nanostructures that may be capable of performing highly selective
  separations with permeabilities comparable to
  NF.~\cite{alexandridis_amphiphilic_2000} The uniform-sized aqueous pores
  characteristic of these types of systems enforce a molecular-size cut-off,
  eliminating issues related to the polydisperity of NF
  pores.~\cite{zhou_supported_2005} In addition to size-exclusion, it may be
  possible to control the chemical environment within the nanopores by altering
  the identities of the hydrophilic moieties that form the pores, affording
  solute-specific separations.~\cite{dischinger_effect_2017}

  %BJC4: bring it back to LLCs but don't make it seem like HII is the best
  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I
  bicontinuous cubic (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010}
  When cross-linked, these materials can function as mechanically strong
  separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} phase
  has hexagonally packed, straight pores which is the ideal geometry for high
  throughtput separations. However, the synthesis of H\textsubscript{II}
  membranes with highly aligned hexagonal mesophases has been a challenge that
  has been met with limited success and has prevented the material's viability as
  a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The
  Q\textsubscript{I} phase consists of a three dimensional network of tortuous
  and interconnected pores.  It's more facile synthesis has yielded it more
  success. The latest Q\textsubscript{I} phase membranes have been shown to
  exhibit selectivities higher than commercial NF and RO membranes with permeabilities
  higher than commercial RO membranes.~\cite{dischinger_application_2017}

  % Highlight that QI has the best chance.
  Although Q\textsubscript{I} membranes have shown promising results, it
  is not clear how to controllably design them for specific separations
  beyond what has already been achieved. Dischinger et al. found that they
  do not separate purely on the basis of size. Empirical modeling revealed
  correlations between various solute physicochemical properties and 
  observed solute rejection. Although there was some agreement with their
  empirical model, it does not offer a sufficiently detailed explanation
  of governing molecular interactions.~\cite{dischinger_effect_2017}

%  Zhou et al. demonstrated complete rejection
%  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
%  membranes.~\cite{zhou_supported_2005}

%  In addition to geometric factors which make H\textsubscript{II} membranes
%  ideal for selective separations, they have the potential to further disrupt
%  conventional membrane separation techniques by being selective based not
%  only on solute size and charge, but on chemical functionality as well. 
%  The functional LLC monomer head groups that occupy the pore region of the
%  membrane can interact with solutes. Dischinger et al.~studied the 
%  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
%  similar pore topology to the H\textsubscript{II} phase, but a more 
%  tortuous geometry, and observed a range of selectivities dependent on the
%  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
%  design of LLC monomers have the potential to help us tailor membranes for 
%  solute-specific separations.

%  While H\textsubscript{II} membranes have been synthesized and characterized
%  in a lab setting, there is a limit to the level of detail that can be obtained 
%  from experiment. These membranes have been primarily characterized with 
%  size-exclusion experiments which can give an estimate of pore size as well as
%  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
%  However, size exclusion does not appear to be sufficient to fully describe LLC
%  membranes. Dischinger et al. studied a similar membrane and found that they do
%  not separate purely on the basis of size.~\cite{dischinger_effect_2017} Empirical modeling revealed correlations
%  between various solute physicochemical properties and observed solute rejection. 
%  Although there was some agreement with their empirical model, it does not
%  offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
%============= 
%  The separation performance of these membranes has been 
%  primarily characterized with size-exclusion experiments which emphasizes 
%  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
%  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
%  %separation BY size exclusion; maybe rephrase?
%  %BJC4: Hmm, by characterization, I mean testing their ability to separate, so I'm 
%  While size-exclusion is a useful separation, it 
%  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
%  important to take advantage of material properties other than pore size. 
%  Unfortunately, this is a more complicated design problem. Experimental transport
%  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
%  unclear trends due to interactions between solutes and pore moieties. Although
%  the authors identified some correlation between select physicochemical properties
%  and solute transport trends, their empirical model does not offer a sufficient 
%  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortunate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?

@@

  %BJC4: also edited here to help with the flow.
  In this work, we present studies of the transport mechanisms exhibited by 20
  uncharged polar solutes with varying size, chemical functionality and
  hydrophilic character within the pores of an H\textsubscript{II} phase LLC
  membrane. The pores of the H\textsubscript{II} phase have a similar topology to
  the Q\textsubscript{I} phase but their geometry is simpler to model. In future
  studies, we will extend our techniques to the Q\textsubscript{I} phase.

  %BJC4: not sure if I should add a thesis to this paragraph, reattach above, or just
  % leave as is since it's informational.
  Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of the
  membrane in which we placed solutes. We have listed the solutes studied along
  with the abbreviations that we will use in the charts for the remainder of this
  paper in Table~\ref{table:abbreviations}. Note that, in order limit our
  studies to uncharged species, we have only studied acetic acid in its
  protonated form. The pKa of gallic acid is 4.40 while the pKa of acetic acid is
  4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} Assuming that the pKa of
  gallic acid is similar to Na-GA3C11, it is possible for our sodium salted
  monomer to exist at the same time as protonated acetic acid. In any case, we
  are more interested in mechanisms of interaction with specific chemical
  functionality more than the behavior of specific molecules.

@@

    \hline
  \end{tabular}
  \caption{Names of solutes along with their molecular structures and the
  abbreviations which we use in this paper. Colors correspond to solute groupings
  and are used in many plots. 
%  Blue corresponds to simple alcohols, red to 
%  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
%  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.
  }\label{table:abbreviations}
  \end{table}

  %MRS2: generally, use present tense for what is being done in the paper, not future tense; 
  %the paper is completely written, later sections are not being written in the future. 
  %MRS2: descriptions of experiments can be in the past.   
  %MRS2: look over this section at the end of the intro again for clarity - some paragraphs are too short (ideas introduced and brushed past quickly) sometimes without strong theses.
  %BJC3: I think these make more sense now.

@@

%  We then present our efforts to understand how water partitions within the pores.  
  We then use the transport rates of water in and out of the pores in order to
  to justify our study of solute transport restricted to the pore region. From a 
  macroscopic perspective, it might make sense to hypothesize that water spends its time 
  exclusively in the tube-like hydrophilic pore region. Our previous work showed
  that there is a gradual compositional transition from the hydrophilic to the
  hydrophobic region which means that solutes may not necessarily stay confined
  to the centers of the pores or even within the pore region. We show that, in 
  our most viable system, water moves fastest within the pores suggesting that 
  the 
  %MR3: added to be more specific - we do look at it getting into the head groups a little.
  area in and around the central
  pores should be the focus of our mechanistic studies.

  %MRS2: ``this information'' is ambiguous. Which information? Also, I'm not sure the paragraph above is enough to 
  %demonstrate why we can/should neglect the tails.
%  We use this information in order to justify our restriction
%  of solute transport studies to just the pore region.

%  We then study the gradient in composition of solutes and 
%  water and any resultant influence it might have on mechanistic properties.

@@

  We simulated water molecules using the TIP3P water model because it is the
  water model that GAFF and other AMBER family parameters have been optmized
  with.~\cite{florova_explicit_2010} %~\cite{mahoney_five-site_2000}

@@

%  We observed that some water partitions into the distal tail region of our system and therefore
%  built our initial configurations with water in both regions, close to the expected
%  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
%  Information). We define the distal tail region to be ca. 1.5 nm from the pore
%  center based on the minimum in the radial distribution function of water
%  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
%  may or may not be experimentally consistent but it is necessary for our results to be 
%  thermodynamically consistent; otherwise, water would slowly leak from the pore into the
%  tail region over several hundred nanoseconds. We iteratively adjusted the pore radius in our systems
%  until the appropriate amount of water fit in the pores after running the GROMACS command
%  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
%  in random locations with a short energy minimization between each insertion. When 
%  studying transport of water in the pores, we limited the calculations to water molecules
%  that spent greater than 95\% of their time outside of the distal tail region. We 
%  justify this decision with better context in Section~\ref{section:transport_water_sodium}.

%  We fully equilibrated an initial solvated configuration before adding solutes. First, we 
%  equilibrated the initial configuration using the `wet' equilibration procedure 
%  described in our previous work. Then we cross-linked the equilibrated solvated 
%  configuration using the cross-linking procedure also described in our previous 
%  work.~\cite{coscia_understanding_2019}

  The equilibrated unit cells have different geometries depending on water
  content. The average distance between pores is 4.15 +/- 0.08 nm and 4.41 +/- 0.07 nm
  in the 5 and 10 wt\% water systems respectively. The length of the pores, accounting
  for tortuosity (see Section~\ref{method:rdfs}), is 9.03 +/- 0.12 nm and 8.07 +/- 0.11
  nm in the 5 and 10 wt\% water systems respectively. The approximate size of the pore
  region increases with water content (see Section~\ref{section:membrane_components}), 
  however we did not quantify the pore radius because its definition is ambiguous. As
  described in our previous work, there is not a hard partition between the pore and tail
  regions.~\cite{coscia_understanding_2019} Rather, there is a gradual transition from 
  the hydrophilic to hydrophobic region.

%  The approximate size of the pore region and the 
%    boundaries we defined are addressed later in the methods and throughout the results and 
%    discussion section.

@@

  We measured the time-averaged $z$-direction (parallel to the pores) mean squared
  displacement (MSD) of the centers of mass (COM) of each solute over the course of 
  1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
    % fully understand the theory since I talk about subdiffusion in terms of 
    % alpha which is always calculated based on ensemble MSD unless we know for sure that
    % the system is ergodic (which it isn't the case for CTRW)
  In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
  by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
  \begin{equation}
	\langle z^2(t) \rangle = \langle z(t) - z(0) \rangle
	\label{eqn:ensemble_msd}
  \end{equation}
  Since the ensemble MSD is calculated with respect to a reference position, it carries
  some dependence on its starting point. The time-averaged MSD averages over all possible
  time lags of a given length, effectively eliminating any initial configuration 
  dependence and generating	an increased number of observations. For ergodic systems, 
  both types of MSDs will be equal. Since we have a small number of solutes with which to
  generate statistics and because we are not calculating values of $\alpha$ for this 
  particular study,	we will only use the time-averaged MSD.

  % BJC: haven't talked about hopping mechanism at this point, but need to justify why
  % I used total MSD rather than fitting some function to it
  We fixed the length of each simulated trajectory so that we could compare the total
  MSD between different solutes without the influence of the ageing phenomenon.
  In systems such as ours where solutes show hopping behavior between long periods 
  of immobility, ageing is defined by the tendency of the average slope of an MSD 
  curve to decrease as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
  Since the maximum measured dwell time can be no longer than the total length of a simulated
  trajectory, longer dwell times are incorporated into the calculation as measurement
  time or trajectory length is increased, lowering the average MSD. Because the solute 
  MSDs are non-linear and because of the ageing phenomenon, we did not attempt to calculate
  a diffusion constant as one might for a Brownian particle with a linear MSD. Instead,
  the reported MSD values represent the average MSD for a given	solute after a 400
  ns time lag. Our results are shown to be insensitive to our choice of time lag in 
  Section~\ref{S-section:lag_sensitivity} of the Supporting Information.

  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear to within 
  statistical precision. Therefore, for the purpose of comparison, we calculated its
  %BJC3: linear within statistical precision --> appears linear? I didn't do any rigorous tests for linearity
  diffusion constant by fitting a line to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured particle displacement in one dimension.

@@

  %MRS4: a bit strange to say you are using Stokes-einstein, but only analyzing MSD's (when MSD's don't appear in that equation)? It could be clarified a bit more.
%  However, this assumes linear behavior
%  of the MSD, which we will show is not that case. Our main usage of the 
%  Stokes-Einstein relationship is to show that solutes in our system do not 
%  behave as it predicts.
  % Possible comps question: Stokes law restricted to Re < 0.1, but we have no flow so Re ~ 0.

>>>>

\title{Chemically Selective Transport in a Cross-Linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}

@@

  The uniform size and complex chemical topology of the pores formed by
  self-assembled amphiphilic molecules such as liquid crystals make them
  promising candidates for selective separations.
  In this work, we observe transport of water, sodium ions and 20 small polar
  solutes within the pores of a lyotropic liquid crystal (LLC) membrane using
  atomistic molecular simulations. We find that the transport of a species is
  dependent not only on molecular size, but on chemical functionality as well.
  The membrane's inhomogeneous composition gives rise to radially dependent
  transport mechanisms with respect to the pore centers. We observe that all
  solutes perform intermittent hops between lengthy periods of entrapment. Three
  different trapping mechanisms are responsible for this behavior. First, solutes
  that drift out of the pore can become entangled among the dense monomer tails.
  Second, solutes can donate hydrogen bonds to the monomer head groups. Third,
  solutes can coordinate with sodium counter ions.  The degree to which a solute
  is affected by each mechanism is dependent on the chemical functionality of the
  solute. Using the insights developed in this study, we can begin to think about
  how to redesign existing LLC membranes in order to perform solute-specific
  separations.

@@

  All of these separations are possible in part with current commercial
  membrane separation techniques, but all still suffer from serious drawbacks.
  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial
  membrane separations of small molecules.~\cite{warsinger_review_2018} RO
  membranes are typically dense polymer matrices that separate solutes based on
  differences in their solubility and permeability in the membrane
  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
  selective separations, high feed pressures and thus large amounts of energy are
  necessary in order to generate a useful permeate
  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
  nm-sized pores which can give the same permeate flux as RO with lower applied
  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
  size, limiting their selectivity.~\cite{werber_materials_2016}.

  Under the right conditions, amphiphilic molecules can self-assemble into
  ordered nanostructures that may be capable of performing highly selective
  separations with permeabilities comparable to
  NF.~\cite{alexandridis_amphiphilic_2000} The uniform-sized aqueous pores
  characteristic of these types of systems enforce a molecular-size cut-off,
  eliminating issues related to the polydisperity of NF
  pores.~\cite{zhou_supported_2005} In addition to size-exclusion, it may be
  possible to control the chemical environment within the nanopores by altering
  the identities of the hydrophilic moieties that form the pores, affording
  solute-specific separations.~\cite{dischinger_effect_2017}

  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I
  bicontinuous cubic (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010}
  When cross-linked, these materials can function as mechanically strong
  separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} phase
  has hexagonally packed, straight pores which is the ideal geometry for high
  throughtput separations. However, the synthesis of H\textsubscript{II}
  membranes with highly aligned hexagonal mesophases has been a challenge that
  has been met with limited success and has prevented the material's viability as
  a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The
  Q\textsubscript{I} phase consists of a three dimensional network of tortuous
  and interconnected pores.  It's more facile synthesis has yielded it more
  success. The latest Q\textsubscript{I} phase membranes have been shown to
  exhibit selectivities higher than commercial NF and RO membranes with permeabilities
  higher than commercial RO membranes.~\cite{dischinger_application_2017}

  Although Q\textsubscript{I} membranes have shown promising results, it
  is not clear how to controllably design them for specific separations
  beyond what has already been achieved. Dischinger et al. found that they
  do not separate purely on the basis of size. Empirical modeling revealed
  correlations between various solute physicochemical properties and 
  observed solute rejection. Although there was some agreement with their
  empirical model, it does not offer a sufficiently detailed explanation
  of governing molecular interactions.~\cite{dischinger_effect_2017}

@@

  In this work, we present studies of the transport mechanisms exhibited by 20
  uncharged polar solutes with varying size, chemical functionality and
  hydrophilic character within the pores of an H\textsubscript{II} phase LLC
  membrane. The pores of the H\textsubscript{II} phase have a similar topology to
  the Q\textsubscript{I} phase but their geometry is simpler to model. In future
  studies, we will extend our techniques to the Q\textsubscript{I} phase.

  Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of the
  membrane in which we placed solutes. We have listed the solutes studied along
  with the abbreviations that we will use in the charts for the remainder of this
  paper in Table~\ref{table:abbreviations}. Note that, in order limit our
  studies to uncharged species, we have only studied acetic acid in its
  protonated form. The pKa of gallic acid is 4.40 while the pKa of acetic acid is
  4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} Assuming that the pKa of
  gallic acid is similar to Na-GA3C11, it is possible for our sodium salted
  monomer to exist at the same time as protonated acetic acid. In any case, we
  are more interested in mechanisms of interaction with specific chemical
  functionality more than the behavior of specific molecules.

@@

    \hline
  \end{tabular}
  \caption{Names of solutes along with their molecular structures and the
  abbreviations which we use in this paper. Colors correspond to solute groupings
  and are used in many plots. 
  }\label{table:abbreviations}
  \end{table}

@@

  We then use the transport rates of water in and out of the pores in order to
  to justify our study of solute transport restricted to the pore region. From a 
  macroscopic perspective, it might make sense to hypothesize that water spends its time 
  exclusively in the tube-like hydrophilic pore region. Our previous work showed
  that there is a gradual compositional transition from the hydrophilic to the
  hydrophobic region which means that solutes may not necessarily stay confined
  to the centers of the pores or even within the pore region. We show that, in 
  our most viable system, water moves fastest within the pores suggesting that 
  the area in and around the central pores should be the focus of our mechanistic studies.

@@

  We simulated water molecules using the TIP3P water model because it is the
  water model that GAFF and other AMBER family parameters have been optimized
  with.~\cite{florova_explicit_2010}

@@

  The equilibrated unit cells have different geometries depending on water
  content. The average distance between pores is 4.15 +/- 0.08 nm and 4.41 +/- 0.07 nm
  in the 5 and 10 wt\% water systems respectively. The length of the pores, accounting
  for tortuosity (see Section~\ref{method:rdfs}), is 9.03 +/- 0.12 nm and 8.07 +/- 0.11
  nm in the 5 and 10 wt\% water systems respectively. The approximate size of the pore
  region increases with water content (see Section~\ref{section:membrane_components}), 
  however we did not quantify the pore radius because its definition is ambiguous. As
  described in our previous work, there is not a hard partition between the pore and tail
  regions.~\cite{coscia_understanding_2019} Rather, there is a gradual transition from 
  the hydrophilic to hydrophobic region. 
  %We observe the same architecture in the systems
  %studied in this paper (see Section~\ref{section:membrane_components}).

@@

  We measured the time-averaged $z$-direction (parallel to the pores) mean squared
  displacement (MSD) of the centers of mass (COM) of each solute over the course of 
  1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.

  In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
  by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
  \begin{equation}
	\langle z^2(t) \rangle = \langle z(t) - z(0) \rangle
	\label{eqn:ensemble_msd}
  \end{equation}
  Since the ensemble MSD is calculated with respect to a reference position, it carries
  some dependence on its starting point. The time-averaged MSD averages over all possible
  time lags of a given length, effectively eliminating any initial configuration 
  dependence and generating	an increased number of observations. For ergodic systems, 
  both types of MSDs will be equal. Since we have a small number of solutes with which to
  generate statistics and because we are not calculating values of $\alpha$ for this 
  particular study,	we will only use the time-averaged MSD.

  We fixed the length of each simulated trajectory so that we could compare the total
  MSD between different solutes without the influence of the ageing phenomenon.
  In systems such as ours where solutes show hopping behavior between long periods 
  of immobility, ageing is defined by the tendency of the average slope of an MSD 
  curve to decrease as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
  Since the maximum measured dwell time can be no longer than the total length of a simulated
  trajectory, longer dwell times are incorporated into the calculation as measurement
  time or trajectory length is increased, lowering the average MSD. Because the solute 
  MSDs are non-linear and because of the ageing phenomenon, we did not attempt to calculate
  a diffusion constant as one might for a Brownian particle with a linear MSD. Instead,
  the reported MSD values represent the average MSD for a given	solute after a 400
  ns time lag. Our results are shown to be insensitive to our choice of time lag in 
  Section~\ref{S-section:lag_sensitivity} of the Supporting Information.

  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear to within 
  statistical precision. Therefore, for the purpose of comparison, we calculated its
  diffusion constant by fitting a line to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured particle displacement in one dimension.

@@

  Since we will be using Equation~\ref{eqn:msd-stokes-einstein} for primarily qualitative observations, 
  we made a number of simplifying assumptions so that it could easily be used for 
  comparison between systems. First, we assume that all systems' viscosities
  are equal since we only make minor changes to the membrane's composition and
  accurately assessing the viscosity in a complex and inhomogeneous system such 
  as ours is a challenge by itself. Second, we assume all particles are approximately
  spherical, neglecting the effect of solute shape on mobility. Chan et al. 
  showed that the difference in diffusion constants of differently shaped 
  particles, with constant molecular volume, did not differ by more than 25\%
  with most deviating by less than 10\%.~\cite{chan_effects_2015}. 
  Third, we assume that the ratio of solute and solvent radii as calculated using the
  methodology of Section~\ref{method:molecular_size}, is equivalent to the the 
  ratio of hydrodynamic radii. For similarly shaped molecules, it has been shown that
  one can relate the hydrodynamic radius and radius of gyration (R\textsubscript{g})
  using a constant scaling factor. \cite{lee_molecular_2008,he_novel_2003,li_critical_2009}.
  Assuming that our end-to-end distance reasonably approximates R\textsubscript{g} 
  for our small, relatively inflexible molecules, we believe this assumption is 
  justified for qualitative demonstrations relevant to this study.

  We fit Equation~\ref{eqn:msd-stokes-einstein} so that it passed through the
  highest solute MSD. We assumed that the solute with the highest MSD exhibited
  the closest to Brownian behavior and therefore could set a rough boundary
  between subdiffusive, Brownian and superdiffusive MSDs. As a lower bound to our
  appoximation, we also plotted the uncorrected version of
  Equation~\ref{eqn:stokes-einstein} ($f$=1), requiring it to converge to the
  same value as the corrected curve for large radii.
